### 2024-05-28 README.Rmd
suggest install via r-universe
add nicer plot and resolve #21

You can install the development version of traveltime from
[GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("idem-lab/traveltime")
```

@@

Et voila!
```{r}
plot(travel_time)
points(from_here, pch = 19, add = TRUE)
```

@@

And where is Changi Airport?
```{r}
changi_airport <- tibble::tibble(
  x = c(103.984),
  y = c(1.355)
)
changi_airport
```
Let's look at those.
```{r}
plot(friction_singapore)
plot(sin, add = TRUE)
points(changi_airport, pch = 19, add = TRUE)
```

@@

Et voi*lah*!
```{r}
plot(travel_time_sin)
points(changi_airport, pch = 19, add = TRUE)
plot(sin, add = TRUE)
```

>>>>

You can install `traveltime` with:

``` r
install.packages("traveltime", repos = c("https://idem-lab.r-universe.dev"))
```

@@

Et voila!
```{r}
plot(travel_time)
points(from_here, pch = 19)
```

@@

And where is Changi Airport?
```{r}
changi_airport <- tibble::tibble(
  x = c(103.984),
  y = c(1.355)
)
changi_airport
```
Let's look at those.
```{r}
plot(friction_singapore)
plot(sin, add = TRUE)
points(changi_airport, pch = 19)
```

@@

Et voi*lah*!
```{r}
plot(travel_time_sin)
points(changi_airport, pch = 19)
plot(sin, add = TRUE)
```

### I want my plots to be nicer
```{r}
library(tidyterra)
library(ggplot2)

ggplot() +
  # plot the spatraster first
  geom_spatraster(
    data = travel_time_sin
  ) +
  theme_minimal() +
  scale_fill_whitebox_c(palette = "deep") +
  # overlay the vector outline
  geom_spatvector(
    data = sin,
    colour = "khaki3",
    linewidth = 1,
    fill = NA
  ) +
  # add the points from tibble
   geom_point(
     data = changi_airport,
     aes(x = x, y = y)
   ) +
  labs(x = NULL, y = NULL, fill = "Travel time\n(minutes)")

```
